---
output: 
  html_document: 
    theme: flatly
authors: Nicolas Rosemberg
---

```{r, include=FALSE}

### 1. Setting Working Directory & Loading the data
# Setting the Working Directory

setwd("/Users/Nico/Documents/Hertie/Thesis/Data analysis/Master-Thesis")

# Loading the Citations
pkgs <- c('ggplot2', 'googleVis', 'plyr')
repmis::LoadandCite(pkgs)

# Loading the merged files from the Working directory
Data <- read.csv(file="website.csv")


```

# MASTER THESIS - DESCRIPTIVE STATISTICS AND FINDINGS



# WHY ARE WE INTERESTED IN THIS TOPIC?  

# DESCRIPTIVE STATISTICS


** Worldwide distribution of out-of-pocket payments **

```{r, results='asis', echo=FALSE, error=FALSE}
OOPMap <- gvisGeoChart(Data, locationvar = 'iso2c',
                        colorvar = 'OOP',
                        options = list(
                          colors = "['#fff7bc', '#d95f0e']"
                        ))

print(OOPMap, tag = 'chart')
```
Source: World Development Indicators
 
** Share of rural population **
```{r, results='asis', echo=FALSE, error=FALSE}
RuralMap <- gvisGeoChart(Data, locationvar = 'iso2c',
                        colorvar = 'Rural',
                        options = list(
                          colors = "['#fff7bc', '#d95f0e']"
                        ))

print(RuralMap, tag = 'chart')
```
Source: World Development Indicators 

** Voice and Accountability **
```{r, results='asis', echo=FALSE, error=FALSE}
VAMap <- gvisGeoChart(Data, locationvar = 'iso2c',
                        colorvar = 'VoiceandAccountability',
                        options = list(
                          colors = "['#fff7bc', '#d95f0e']"
                        ))

print(VAMap, tag = 'chart')
```
Source: Worldwide Governance Indicators 

** Government Effectiveness **
```{r, results='asis', echo=FALSE, error=FALSE}
GEMap <- gvisGeoChart(Data, locationvar = 'iso2c',
                        colorvar = 'GovernmentEffectiveness',
                        options = list(
                          colors = "['#fff7bc', '#d95f0e']"
                        ))

print(GEMap, tag = 'chart')
```
Source: Worldwide Governance Indicators 

** Political Stability and No Violence **
```{r, results='asis', echo=FALSE, error=FALSE}
PSMap <- gvisGeoChart(Data, locationvar = 'iso2c',
                        colorvar = 'PoliticalStabilityNoViolence',
                        options = list(
                          colors = "['#fff7bc', '#d95f0e']"
                        ))

print(PSMap, tag = 'chart')
```
Source: Worldwide Governance Indicators 

** Freedom **
```{r, results='asis', echo=FALSE, error=FALSE}
FreeMap <- gvisGeoChart(Data, locationvar = 'iso2c',
                        colorvar = 'Free',
                        options = list(
                          colors = "['#fff7bc', '#d95f0e']"
                        ))

print(FreeMap, tag = 'chart')
```
Source: Freedom House

** Gender Equality **
```{r, results='asis', echo=FALSE, error=FALSE}
GQMap <- gvisGeoChart(Data, locationvar = 'iso2c',
                        colorvar = 'GenderEquality',
                        options = list(
                          colors = "['#fff7bc', '#d95f0e']"
                        ))

print(GQMap, tag = 'chart')
```
Source: World Development Indicators
 
 
For a better understanding of the dynamics of our datasets, feel free to play with the following interactive tool: 

```{r, results='asis', echo=FALSE, error=FALSE}

M <- gvisMotionChart(Data, "Country", "year",
                     options=list(width=900, height=650))


print(M, tag = 'chart')

```




# FINDINGGS



